### 2020-04-30 manuscript.rmd
Format HTML table rownames.
Fix typo.

### Materials & Methods  
#### Study Design  
We performed a case-crossover study to define the relationship between the quantity of sputum production (primary exposure), measured as the frequency with which nurses and respiratory therapists chose to perform as-needed subglottic suctioning, and the occurrence of VAE (primary outcome). We also analyzed whether VAE were categorized as VAC without suspected infection or as IVAC. For the primary anlysis, the day of VAE was the case period; the days prior to VAE were the control periods.

@@

#### Availability of Data  
Data, model code, and code used to produce the figures is available at https://github.com/bjklab/Sputum-quantity-and-adverse-events-during-mechanical-ventilation.

>>>>

### Materials & Methods  
#### Study Design  
We performed a case-crossover study to define the relationship between the quantity of sputum production (primary exposure), measured as the frequency with which nurses and respiratory therapists chose to perform as-needed subglottic suctioning, and the occurrence of VAE (primary outcome). We also analyzed whether VAE were categorized as VAC without suspected infection or as IVAC. For the primary analysis, the day of VAE was the case period; the days prior to VAE were the control periods.

@@

#### Availability of Data  
Data, model code, and code used to produce the figures are available at https://github.com/bjklab/Sputum-quantity-and-adverse-events-during-mechanical-ventilation.
